How does the frequency and duration of social media usage correlate with indicators of mental health, such as anxiety and depression, among adolescents aged 13-19?

### 2024-04-17 output/paper/paper.qmd
made more relevant graphs and readings

Correlation analysis revealed a statistically significant positive correlation between the frequency and duration of social media usage and the levels of anxiety and depression among adolescents. Figure 2 depicts the correlation between the duration of social media usage and anxiety levels among adolescents, providing a visual representation of this noteworthy relationship.

@@

@@

Subgroup analysis showcased that the association between social media usage and mental health outcomes varied depending on demographic factor such as age. Figure 3 visually portrays the divergence in social media usage duration across different age groups, shedding light on the nuanced relationship between social media engagement and age demographics.

@@

Furthermore, Figure 2, a scatter plot, demonstrates the correlation between social media usage duration and anxiety levels among adolescents. This graphical representation elucidates the relationship between the two variables, emphasizing the potential impact of prolonged social media exposure on mental well-being.

Additionally, Figure 3, a box plot, illustrates the variation in social media usage duration across different age groups. By visually comparing the distribution of usage duration among various age cohorts, this visualization aids in identifying any age-related patterns or trends in social media consumption habits.

>>>>

Correlation analysis revealed a statistically significant positive correlation between the frequency and duration of social media usage and the levels of anxiety and depression among adolescents. Figure 2 depicts the correlation between the duration of social media usage and anxiety levels among adolescents, providing a visual representation of this noteworthy relationship. Figure 3 depicts the correlation between the duration of social media usage and depression levels among adolescents, providing a visual representation of this noteworthy relationship.

@@

```{R}
#| echo: false
#| fig-cap: Scatter plot showing the correlation between social media usage duration and depression levels among adolescents
# Graph 2_1: Scatter plot showing the correlation between social media usage duration and depression levels among adolescents
graph2_1 <- ggplot(data, aes(x = Social_Media_Duration, y = Depression_Score)) +
  geom_point(color = "green") +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  labs(title = "Correlation between Social Media Usage Duration and Depression Levels",
       x = "Social Media Usage Duration per day",
       y = "Depression Score(out of 100)") +
  theme_minimal()
print(graph2_1)
```

@@

Subgroup analysis showcased that the association between social media usage and mental health outcomes varied depending on demographic factor such as age. Figure 4 visually portrays the divergence in social media usage duration across different age groups, shedding light on the nuanced relationship between social media engagement and age demographics.

@@

Furthermore, Figure 2 and Figure 3, scatter plots, demonstrates the correlation between social media usage duration and anxiety and depression levels among adolescents. This graphical representation elucidates the relationship between the two variables, emphasizing the potential impact of prolonged social media exposure on mental well-being.

Additionally, Figure 4, a box plot, illustrates the variation in social media usage duration across different age groups. By visually comparing the distribution of usage duration among various age cohorts, this visualization aids in identifying any age-related patterns or trends in social media consumption habits.
